Abstract

### 2025-10-03 output/Main_text.Rmd
Fine tune figure 1 output
Set axis lines and limits properly.

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     5
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_oblique_ls)

ggsave(file.path(DOC_DIR, "Figure_1.svg"), width = 6.65, height = 5)
```

>>>>

```{r item-plot-out}
#| cache:          false
#| fig.cap:   Item Plots in an Orthogonal (Left) and Oblique (Right) Test Space
#| fig.topcaption: true
#| fig.height:     5.2
#| fig.width:      6.65
#| warning:        false
(plot_orth_uncorr_contours + plot_orth_corr) /
  (plot_oblique_ts + plot_oblique_ls) +
  plot_layout(guides = "collect")
## TODO: Review and reformat axis labels

ggsave(file.path(DOC_DIR, "Figure_1.svg"), width = 6.65, height = 5.2)
```
